Homework 7 - Stat 495

### 2022-11-01 homework/hmk7/hmk7Stat495F22.Rmd
Just have Add 4 left

SOLUTION: This variable is not very useful for this analysis because from the histogram below, there are significantly more observations with a value of 0 than a value of 1. Additionally, there are no observations with a value of 1 for `QikProp_.amidine` that "do not cross" the blood-brain barrier and only 1 observation of `QikProp_.amidine` value 1 that "crosses" the blood-brain barrier.

@@

# set 1 to be "crosses" and 0 to be "does not cross"
train2 <- mutate(train, Class = ifelse(Class == "Crosses", 1, 0))

@@

boost_estimate <- predict(class.boost, newdata = train2, n.trees = 500, 
                          type = "response")

pred_class <- boost_estimate > 0.5
tally(~ pred_class)

table(train2$Class, pred_class)

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

SOLUTION: This variable is not very useful for this analysis because there are significantly more observations with a value of 0 than a value of 1. Additionally, there are no observations with a value of 1 for `QikProp_.amidine` that "do not cross" the blood-brain barrier and only 1 observation of `QikProp_.amidine` value 1 that "crosses" the blood-brain barrier.

@@

# set 1 to be "crosses" and 0 to be "does not cross"
train2 <- mutate(train, Class = ifelse(Class == "Crosses", 1, 0))
test2 <- mutate(test, Class = ifelse(Class == "Crosses", 1, 0))

@@

boost_estimate_train <- predict(class.boost, newdata = train2, n.trees = 500, 
                          type = "response")

pred_class_train <- ifelse(boost_estimate_train > 0.5, 1, 0)
tally(~ pred_class_train)

table(train2$Class, pred_class_train)

@@

# for boosting model
test2 <- mutate(test, Class = ifelse(Class == "Crosses", 1, 0))
boost_estimate_test <- predict(class.boost, newdata = test2, n.trees = 500, 
                          type = "response")
pred_class_test <- ifelse(boost_estimate_test > 0.5, 1, 0)
table(test2$Class, pred_class_test)
(8+7)/(8+7+7+2)

```
 The Bagging model appears to have an accuracy of 75% on the test set. The Random Forest model appears to have an accuracy of 66.7% on the test set and the Boosting model appears to have an accuracy of 62.5% on the test set. Therefore, we would choose the Bagging model for predicting Class because the model had the higest accuracy.

@@

```{r}
set.seed(1)
nnet_class <- nnet(Class ~ ., train, size = 15)

trainpred <- predict(nnet_class, type = "class")
tally(Class ~ trainpred, data = train)
```

@@

```{r}
set.seed(1)
nnet_class2 <- nnet(Class ~ ., train, size = 15, decay = 5e-4)

trainpred2 <- predict(nnet_class2, type = "class")
tally(Class ~ trainpred2, data = train)

@@

```{r}
set.seed(1)
nnet_class3 <- nnet(Class ~ ., train, size = 15, decay = 5e-4, maxit = 1030)

trainpred3 <- predict(nnet_class3, type = "class")
tally(Class ~ trainpred3, data = train)

@@

SOLUTION: We will do the same as we did before and compare models based on their accuracy in predicting the test set.

```{r}
# neural net 1
pred <- predict(nnet_class, newdata = test, type = "class")
tally(Class ~ pred, data = test)
(8+8)/(8+8+6+2)

# neural net 2
pred2 <- predict(nnet_class2, newdata = test, type = "class")
tally(Class ~ pred2, data = test)
(9+8)/(9+8+1+6)

# neural net 3
pred3 <- predict(nnet_class3, newdata = test, type = "class")
tally(Class ~ pred3, data = test)
(8+8)/(8+8+6+2)
```

From the confusion matrices above, it appears the the accuracy in predicting the test set from our first and third neural network model is 66.7% and the accuracy in predicting the test set from the second model is 70.8%. This means that we would choose the second neural network for predicting the test set. However, it is important to note that the difference between the accuracy in all of these models is only one more correct observation which could could change depending on the seed.

@@

```{r}
set.seed(1)
svm1 <- svm(Class ~ ., data = train, gamma = 0.75, kernel = "radial")
summary(svm1)
```

@@

```{r}
set.seed(1)
svm2 <- svm(Class ~ ., data = train, gamma = 0.5, kernel = "poly")
summary(svm2)
```

@@

```{r}
set.seed(1)
svm3 <- svm(Class ~ ., data = train, gamma = 0.0001, kernel = "poly")
summary(svm2)
```

@@

SOLUTION: Again, we will use the confusion matrices to determine how accurate each model is at predicting the test set.

```{r}
# for svm1
svm1predtest <- predict(svm1, test)
tally(Class ~ svm1predtest, data = test)
(14+0)/(14+10)

# for svm2
svm2predtest <- predict(svm2, test)
tally(Class ~ svm2predtest, data = test)
(9+8)/(9+8+5+2)

# for svm2
svm3predtest <- predict(svm3, test)
tally(Class ~ svm3predtest, data = test)
(14+0)/(14+10)
```

It appears the that first and third SVM model predict the test set with an accuracy of 58.3% while the second model predicts the test set with a 70.8% accuracy.

@@

SOLUTION: Between the three models that we picked as the best for each section, the Bagging model was the most accurate at predicting the test set at 75%. However, this corresponds to 6 mistakes and best models for the Neural Net and SVM sections only had 7 mistakes. Due to the test set being so small, it is difficult to determine which model is the best because even a change of the seed value could cause a different model to have a higher accuracy rate. This means that we would choose the Bagging model as our final model to predict Class with these concerns in mind.
